The Impact of Alternation

### 2017-05-15 draft.tex
ok

We have implemented both Algorithm \ref{alg:predabs} and
\ref{alg:impact} in a prototype tool\footnote{\url{XXXX}} that uses
the Z3 SMT solver\footnote{\url{https://github.com/Z3Prover/z3}} to
check satisfiability queries and generate interpolants in the theory
of linear integer arithmetic variables (LIA). We compared both
algorithms with a previous implementation of trace inclusion
procedure, called
\textsc{Includer}\footnote{\url{http://www.fit.vutbr.cz/research/groups/verifit/tools/includer/}},
that uses on-the-fly determinisation and lazy predicate abstraction
with interpolant-based refinement \cite{Tacas16}.

>>>>

We have implemented both Algorithm \ref{alg:predabs} and
\ref{alg:impact} in a prototype tool\footnote{\url{IMPLEMENTATION URL}} that uses
the Z3 SMT solver\footnote{\url{https://github.com/Z3Prover/z3}} to
check satisfiability queries and generate interpolants in the theory
of linear integer arithmetic variables (LIA). We compared both
algorithms with a previous implementation of trace inclusion
procedure, called
\textsc{Includer}\footnote{\url{http://www.fit.vutbr.cz/research/groups/verifit/tools/includer/}},
that uses on-the-fly determinisation and lazy predicate abstraction
with interpolant-based refinement \cite{Tacas16}.
